Fast Algorithms for Intersection of Nonmatching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex
Finish afront algorithm description.

Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
elements of the same lower dimension (1D, 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).

@@

Now that we have provided the first candidate pair, we can look at the scheme in \fig{fig:prolongation} and see us moving from the green box in the left upper corner. If there exists an intersection, we start a new component and
we can procced to tracking the intersection. Otherwise, we select another 1D or 2D element and start over.

@@

The advancing front algorithm works the same way for both 1D and 2D components and is displayed by the scheme in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all 
possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes in \fig{fig:prolongation}). We shall now describe the algorithm in detail.

@@

>>>>

Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
elements of the same lower dimension (1D, or 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).

@@

Now that we have provided the first candidate pair, we can look at the scheme in \fig{fig:prolongation} and see us moving from the green box in the left upper corner. If an intersection exists, we have just started a new component and we can procced to tracking the intersection. Otherwise, we select another 1D or 2D element and start over.

@@

Let us now discuss the advancing front algorithm displayed by the scheme in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes).

@@

\notePE{We can discuss further the covering/closing of the elements and component numbering which is not tested
thoroughly at the moment. We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3D elements).}
